On multilevel constraint decomposition methods \\ for nonlinear and nonlocal variational inequalities

### 2021-07-07 paper/mcd2.tex
Bits of thinking.

\begin{assumptions}  \emph{Lipschitz restrictions}: There exists $C_1>0$ so that
\begin{equation}
\left(\sum_{i=0}^{m-1} \|R_i u - R_i v\|^2\right)^{1/2} \le C_1 \|u-v\| \label{as:lipschitzrestrictions}
\end{equation}
for all $u,v\in\cK$.  \emph{Totally Lipschitz residual}: There exists $C_2>0$ so that
\begin{equation}
FIXME \label{as:totallylipschitzresidual}
\end{equation}
for all 
\end{assumptions}

>>>>

\begin{assumptions}  \emph{Lipschitz restrictions}: There exists a constant $C_1>0$ so that
\begin{equation}
\left(\sum_{i=0}^{m-1} \|R_i u - R_i v\|^2\right)^{1/2} \le C_1 \|u-v\| \label{as:lipschitzrestrictions}
\end{equation}
for all $u,v\in\cK$.  \emph{Totally Lipschitz residual}: There exists $C_2>0$ so that
\begin{equation}
FIXME \label{as:totallylipschitzresidual}
\end{equation}
for all FIXME
\end{assumptions}
Note that the constants $C_1,C_2$ generally depend on $m$.  % IF PROOF BELOW SUCCEEDS, SO ALGORITHM IS NORM DECREASING, THEN MAY BE ABLE TO ARGUE THAT IT IS O.K. FOR CONSTANTS TO DEPEND ON $u,v,w_{ij}$ etc. AS LONG AS THEY ARE UNIFORMLY BOUNDED ON CERTAIN BOUNDED SETS
